Tennis doubles and ghosts

### 2021-02-04 inst/tennis.Rmd
better docs

```{r}
(hess1 <- hessian(tennis,indep(tennis_maxp),border=TRUE))
(hess2 <- hessian(tennis,indep(tennis_maxp),border=FALSE))
eigen(hess2,TRUE,TRUE)
```

>>>>

We can use the Hessian matrix:

```{r}
(M <- hessian(tennis,indep(tennis_maxp),border=TRUE))
```

See how the fillup value `p4` takes up the unit sum constraint [it is
defined as $p_4=1-p_1-p_2-p_3$].  Matrix `M` should be
negative-semidefinite:

```{r}
eigen(M,TRUE,TRUE)$values # one value is zero to numerical precision; the rest should be <0
```

See how one eigenvalue is zero (to numerical precision) and the rest
are strictly negative, corresponding to the support function having a
well-defined maximum.
